Hydras \& Co.

### 2022-11-21 doc/chapter-fol.tex
minor changes, bullets in folLogic

In order to get more readable terms and formulas, we can define a few notations in ~\href{../theories/html/hydras.MoreAck.FOL_notations.html}{MoreAck.FOL\_notations} and
~\href{../theories/html/hydras.Ackermann.LNN_notations.html}{MoreAck.LNN\_notations}.

>>>>

In order to get more readable terms and formulas, we can define a few notations in ~\href{../theories/html/hydras.MoreAck.FOL_notations.html}{MoreAck.FOL\_notations} and
~\href{../theories/html/hydras.MoreAck.LNN_notations.html}{MoreAck.LNN\_notations}.
Please note that these notation scopes are experimental: We are going to use them in examples and exercises before using them in large original proof scripts (in the \texttt{ordinals/Ackermann/} sub-directory).

We try to define notation scopes as close as possible to \coq's syntax for propositions.

Let us take for instance the following proposition (in math form):

$$\forall\, v_0,\, v_0=0\vee \exists\,v_1,\,v_1=1+v_0$$

Here is a definition, using directly the \texttt{goedel/Ackermann}'s project syntax.

\inputsnippets{LNN_Examples/uglyF0}

Note that, because of redefinitions, the disjonction \texttt{orH}
can be expanded in terms of  implication and negation (for instance when we use \texttt{Compute}).

\inputsnippets{LNN_Examples/uglyF0a}

\inputsnippets{LNN_Examples/CNNF0}
